\section[5]{Conclusion}

\begin{frame}{Conclusion}
\textbf{Adaptive SPS} extending Storm
\begin{itemize}
	\item \textbf{Pool of replicas}
	\item \textbf{Load-aware grouping}
\end{itemize}
	
Two approaches:
\begin{itemize}
	\item \textbf{Reactive (RA-SPS)} : Use of a multi-metric
	\item \textbf{Predictive (PA-SPS)} : Estimate number of active replicas using different predictive models
\end{itemize}
\end{frame}

\begin{frame}{Future work}
Dynamic adaptation of parameters
	\begin{itemize}
		\item RA-SPS uses different parameters, which can be adjusted by AI
	\end{itemize}
	
Hybrid adaptive SPS
	\begin{itemize}
		\item Use the reactive and predictive model for SPS adaptation
	\end{itemize}

Physical and logical adaptation
	\begin{itemize}
		\item Consider also the modification of virtual machines
	\end{itemize}
\end{frame}

\begin{frame}{}

	{\Huge Merci beaucoup !}
\end{frame}

\begin{frame}{Publications}
\footnotesize

\begin{itemize}
	\item[-] [\cite{WladdimiroNCA}] Daniel Wladdimiro, Luciana Arantes, Pierre Sens and Nicolas Hidalgo. "A Multi-Metric Adaptive Stream Processing System." In: NCA. IEEE, 2021.
	\item[-] [\cite{WladdimiroSBAC}] Daniel Wladdimiro, Luciana Arantes, Pierre Sens and Nicolas Hidalgo. "A predictive approach for dynamic replication of operators in distributed stream processing systems" In: SBAC. IEEE, 2022.
	\item[-] [\cite{WladdimiroJPDC}] Daniel Wladdimiro, Luciana Arantes, Pierre Sens and Nicolas Hidalgo. "PA-SPS: A Predictive Adaptive Approach for an Elastic Stream Processing System" In: JPDC. 2023. [Minor Revision]
	\item[-] [\cite{WladdimiroComPAS2022}] Daniel Wladdimiro, Luciana Arantes, Pierre Sens and Nicolas Hidalgo. "A predictive model for Stream Processing System that dynamically calibrates the number of operator replicas." In: ComPAS. Amiens, France, 2022.
	\item[-] [\cite{WladdimiroComPAS2023}] Daniel Wladdimiro, Luciana Arantes, Pierre Sens and Nicolas Hidalgo. "PRESPS: a PREdictive model to determine the number of replicas of the operators in Stream Processing Systems" In: ComPAS. Annecy, France,
2023.
\end{itemize}
\end{frame}

